In our first example (Program \ref{Hypre_SolveEx.cpp}), we will examine how
to use hypre solvers and preconditioners with Tpetra objects.

\begin{lstinputlisting}[caption=Hypre\_SolveEx.cpp,label=Hypre_SolveEx.cpp]{src/Hypre_SolveEx.cpp}
\end{lstinputlisting}

\paragraph{Lines 1--8}
Include statements

\paragraph{Lines 11--28}
Typedefs and using statements to make the code more readable

\paragraph{Lines 31--36}
Set up MPI

\paragraph{Lines 39--48}
Parse command line arguments.  This program allows the user to specify how large
the problem should be, how accurately the linear system should be solved, and
how much information should be printed.

\paragraph{Lines 51--86}
Set up the 2D Laplace operator.

\paragraph{Lines 89--93}
Create a random right-hand-side and initialize the solution vector to 0.

\paragraph{Lines 96--106}
Set hypre options (documented in the hypre user and reference manuals found at
\url{http://computation.llnl.gov/project/linear_solvers/software.php}). In this
example, we have elected to use the conjugate gradient method with an algebraic
multigrid preconditioner.  We have specified a particular coarsening and
relaxation type.  The most important thing to note about BoomerAMG is that if
you would like to use it as a preconditioner, you must set its maximum number of
iterations to 1; otherwise, hypre will assume you meant to use it as a linear
solver.  We then set the tolerance and maximum number of iterations for hypre's
conjugate gradient solver.

\paragraph{Lines 109--118}
Create the hypre solver.  Line 111 specifies that we will be using a hypre
linear solver, and line 112 says it will be the conjugate gradient method.  Line
113 says we would also like to use BoomerAMG.  Remember that you must also set
``SetPreconditioner'' to true, or the preconditioner will not be used.  Lines
115 and 116 specify the hypre parameters such as print level, tolerance, and
maximum number of iterations.

\paragraph{Line 121}
Solve the linear system.  The function ``apply'' actually calls the hypre linear
solve routine PCG with a BoomerAMG preconditioner, as we specified above.