\section{Trilinos-PETSc}
There is a two-way interface between PETSc and Trilinos which allows users to
use PETSc datatypes with Trilinos and vice-versa.

\subsection{Using PETSc Mat and Vec with Trilinos solvers}
Trilinos has two new interfaces to support using PETSc Mat anywhere
a Tpetra::RowMatrix or Tpetra::CrsMatrix can be used.  For packages requiring a
Tpetra::RowMatrix or Tpetra::Operator, such as Anasazi and Belos, you may wrap a
PETSc Mat in a Tpetra::PETScAIJMatrix; otherwise, you can copy it to a
Tpetra::CrsMatrix.  We will demonstrate each of those functions in the examples
below.

\input{petsc_example1}

\input{petsc_example2}

\subsubsection{Is the data copied or wrapped?}
If you are using a part of Trilinos that requires Operator or RowMatrix, the
data is wrapped.  If you need a CrsMatrix specifically, the data is deep-copied.

\subsection{Using Trilinos datatypes with PETSc KSP solvers}
If you would like to use Trilinos datatypes, such as Tpetra::Operator and
Tpetra::MultiVector, with a PETSc KSP linear solver, you may use the new
Belos\footnote{Belos is the iterative solver package of Trilinos.} interface:
PETScSolMgr.  This interface is very similar to that of the other native Belos
linear solvers, which makes solving linear systems such as $AX=B$ a simple
process.

\begin{enumerate}
  \item (Optional) Create a Tpetra::Operator for the preconditioner $M \approx
  A$.  You may use the preexisting preconditioners of Ifpack2 and MueLu, or you
  may create your own custom preconditioner.  Alternatively, you may choose not
  to use a preconditioner at all.
  \item Create a Belos::LinearProblem containing the operator $A$, the initial
  guess $X$, the right-hand side $B$, and the preconditioner $M$ (if you have
  one).
  \item Create a Teuchos::ParameterList containing the parameters you wish to
  set.  These parameters are summarized in Table \ref{table:ksp_parameters}.
  \item Create a Belos::PETScSolMgr with the LinearProblem and ParameterList
  from the previous steps.
  \item Call solve()
\end{enumerate}

\begin{table}
\center
\begin{tabular}{p{.9in} p{3.5in} c}
  \hline
  Parameter & Description & Default Value \\
  \hline
  Maximum Iterations & integer defining the maximum number of iterations to be
  performed. & 1000 \\
  \hline
  Solver & string defining the linear solver to be used. A list of all valid
  linear solver options can be found at
  \url{http://www.mcs.anl.gov/petsc/petsc-current/docs/manualpages/KSP/KSPType.html}
  & KSPGMRES \\
  \hline
  Verbosity & Belos::MsgType defining the amount of output the program should
  produce. Options include Belos::Errors, Belos::Warnings,
  Belos::IterationDetails, Belos::TimingDetails, and Belos::StatusTestDetails &
  Belos::Errors
  \\
  \hline
  Convergence Tolerance & double defining the tolerance of the linear solver &
  $10^{-8}$
  \\
  \hline
\end{tabular}
\caption{Belos::PETScSolMgr parameters}
\label{table:ksp_parameters}
\end{table}

\input{petsc_example3}

\subsubsection{Can I use this to solve linear systems with multiple
right-hand sides?}
Yes.  Unfortunately, PETSc has no support for multivectors at
this time, so each of the right hand sides will be processed independently.
If you want block or pseudo-block linear solvers, those are available within
Trilinos.

\subsubsection{Is the data copied or wrapped?}
The raw Tpetra matrix (or operator) data is wrapped rather than deep copied. 
The same applies to the preconditioner, if you are using a preconditioner.
