\section{Trilinos-SuperLU}

Trilinos has a Tpetra-based interface to SuperLU-Dist in the sparse
factorization package Amesos2.  All Amesos2 solvers can be used the
following way:

\begin{enumerate}
  \item Create the solver using the Amesos2 solver factory, which takes as input
  a string denoting which solver is to be used (KLU2, MUMPS, PARDISO, etc) and
  the matrix to be factored.
  \item Set the parameters for that solver (optional)\footnote{Parameters are
  documented at
  \url{https://trilinos.org/docs/dev/packages/amesos2/doc/html/group__amesos2__solver__parameters.html}}
  \item Perform a symbolic factorization based on the sparsity pattern of the
  matrix
  \item Perform a numeric factorization based on the entries of the matrix.  If
  the matrix's values changed, this factorization must be performed again.
  \item Set the initial guess and right-hand side vectors.
  \item Solve the linear system.  Note that multiple solves can be done without
  needing to refactor the matrix.
\end{enumerate}

There are numerous examples on the Amesos2 Doxygen page
(\url{https://trilinos.org/docs/dev/packages/amesos2/doc/html/examples.html})
We now present one such example demonstrating how to use this interface to solve
a sparse linear system.

\begin{lstinputlisting}[caption=SuperLU\_Amesos2Ex.cpp,label=SuperLU_Amesos2Ex.cpp]{src/SuperLU_Amesos2Ex.cpp}
\end{lstinputlisting}

\paragraph{Lines 1--31}
Include statements and typedefs

\paragraph{Lines 33--35}
Initialize MPI

\paragraph{Lines 41--66}
Create a map describing the parallel distribution of the matrix rows.  Then,
create the matrix, specifying that each row will have at most three entries.  We
then set the entries of the matrix by calling insertGlobalValues.

\paragraph{Lines 68--90}
Create the initial guess and right-hand side vector.  The initial guess $X$ will
be overwritten by the solution computed by SuperLU\_Dist.

\paragraph{Lines 92--116}
Ask Amesos2 whether SuperLU\_Dist has been enabled.  If so, create a
SuperLU\_Dist solver using the Amesos2 solver factory.  Note that the interface
is the same regardless of the solver; if you wished to use Amesos2's native KLU2
solver, you would simply replace ``SuperLU\_DIST'' in lines 93 and 96 with
``KLU2''.  Perform a symbolic factorization, numeric factorization, then a
linear solve.  
